Notes for Week 8/26/2020 - 9/2/2020

### 2020-09-04 notes/weekly_notes/8.26.20.NotesForWeek.tex
Many changes to the graph regression paper. Most fundamentally, I have added a section in which we go through our results on graph Sobolev classes: we will see if this was a good choice.

\section{Bounds on the graph Sobolev semi-norm}
In this section we will state and prove three different Lemmas involving the graph Sobolev semi-norm $f_0 \Lap_{n,r}^s f_0$. In each Lemma, we will derive that the asymptotic relation
\begin{equation*}
f_0^T \Lap_{n,r}^s f_0 \lesssim n \bigl(nr^{d + 2}\bigr)^s
\end{equation*}
holds with high probability, whenever $r \to 0$ sufficiently slowly as $n \to \infty$. The difference between the three Lemmas will be the assumptions we make, and the resulting permissible range for $r$. Throughout, we will make heavy use of Taylor's Theorem, which we briefly recall. For an open set $U \subseteq \Reals^d$ and a function $g \in C^{\infty}(U)$, it holds that for all $x,x' \in U$, and for every $s \geq 1$,
\begin{equation*}
g(x') = \sum_{\abs{\alpha} = 0}^{s - 1} g^{(\alpha)}(x) \cdot (x' - x)^{\alpha}  + R_g^{(s)}(x',x)
\end{equation*}
where for concision we have written 
\begin{equation*}
g^{(\alpha)}(x) = \frac{1}{\abs{\alpha}!} \bigl(D^{\alpha}g\bigr)(x),~~ R_g^{(s)}(x',x) = \frac{1}{s!} \sum_{\abs{\alpha} = s} (x' - x)^{\alpha} \int_{0}^{1} (1 - t)^{\abs{\alpha}}  g^{(\alpha)}\bigl(x + t(x' - x)\bigr) \,dt
\end{equation*}
and $x^{\alpha} = \prod_{i = 1}^{d} x_i^{\alpha_i}$ for $x,\alpha \in \Reals^d$.

\subsection{First-order graph Sobolev semi-norm.}
We begin by upper bounding $f_0^T \Lap_{n,r} f_0$ under the assumption $f_0 \in H^1(\Xset,M)$. This will be the easiest of the three Lemmas to prove, while still giving some sense of how the proofs develop in the more complicated cases. The upper bound will depend on the kernel $K$; we assume throughout that $K:[0,\infty) \to [0,\infty)$ has support on $[0,1]$ with
\begin{equation*}
\int_{\Reals^d} K(\norm{z}) \,dz = 1,
\end{equation*}
and we let
\begin{equation*}
I_{\alpha} := \int_{B(0,1)} (z)^{\alpha} K\bigl(\norm{z}\bigr) \,dz
\end{equation*}
where $B(0,1) \subseteq \Reals^d$ is the unit ball centered at the origin.
\begin{lemma}
	\label{lem:first_order_graph_sobolev_seminorm}
	Suppose $\Xset$ is a Lipschitz domain, and that $p(x) \leq p_{\max}$ for all $x \in \Xset$. Then, for any $f \in H^1(\Xset,M)$, there exists a constant $C > 0$ which may depend only on $\Xset$ and $d$ such that
	\begin{equation}
	f^T \Lap_{n,r} f \leq \frac{C}{\delta} n^2 r^{d + 2} M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{proof}
	We will show that
	\begin{equation*}
	\Ebb\Bigl[f^T \Lap_{n,r} f\Bigr] \leq C n^2 r^{d + 2} M^2,
	\end{equation*}
	whence the claim follows immediately by Markov's inequality (recall that $\Lap_{n,r}$ is positive semi-definite, and therefore $f^T \Lap_{n,r} f$ is a non-negative random variable).

@@

\subsection{General graph Sobolev semi-norm}

When $s > 1$, in order to obtain the desired upper bound on the graph Sobolev semi-norm we must make some additional assumptions regarding the behavior of $f_0$ near the boundary of $\Xset$, as well as on the smoothness of the density function $p$.
\begin{theorem}
	\label{thm:graph_sobolev_seminorm}
	Suppose $\Xset $ is a Lipschitz domain, and that the density $p \in C^{s - 1}(\Xset,p_{\max})$. Then, for any $f \in H_0^s(\Xset,M)$ there exists a constant $C > 0$ which may depend only on $X$ and $d$ such that
	\begin{equation}
	\label{eqn:graph_sobolev_seminorm}
	f^T \Lap_{n,r}^s f \leq \frac{C}{\delta} n^{s + 1} r^{s(d + 2)}M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{theorem}
The proof of Lemma~\ref{thm:graph_sobolev_seminorm} will be considerably longer than that of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}. In anticipation of this proof, it will be helpful to introduce some notation. For $j \in [n]$ and a function $f: \Xset \to \Reals$, define the weighted difference operator $D_jf: \Xset \to \Reals$ to be
\begin{equation*}
\bigl(D_jf\bigr)(x) = \bigl(f(X_j) - f(x)\bigr) \frac{K_r(X_j,x)}{r^d},
\end{equation*}
and for $k \in [n]^q$ for some $q \in \mathbb{N}$, define the iterated difference operator $D_{jk}f: \Xset \to \Reals$ via the recursive formula
\begin{equation*}
\bigl(D_{jk}f\bigr)(x) = \bigl(D_j \circ D_kf\bigr)(x)
\end{equation*}
The matrix $\Lap_{n,r} \in \Reals^{n \times n}$ can then be extended to an operator over $C^{\infty}(\Xset)$, which in an abuse of notation\footnote{We repeat notation because it results in \eqref{eqn:graph_Laplacian_out_of_sample} agreeing with \textcolor{red}{(2)} in-sample, i.e. $\bigl(\Lap_{n,r}^qf\bigr)(X_i) = (\Lap_{n,r}^qf)_i$ for all $i \in [n]$.} we also denote by $\Lap_{n,r}$,
\begin{equation*}
\frac{1}{r^d}\bigl(\Lap_{n,r}f\bigr)(x) := -\sum_{j = 1}^{n} \bigl(D_jf\bigr)(x)
\end{equation*}
so that
\begin{equation}
\label{eqn:graph_Laplacian_out_of_sample}
\frac{1}{r^{dq}}\bigl(\Lap_{n,r}^qf\bigr)(x) = (-1)^q \sum_{k \in [n]^q} \bigl(D_kf\bigr)(x).
\end{equation} 
Consequently, a few standard computations show that the graph Sobolev semi-norm can be written as 
\begin{equation*}
f^T \Lap_{n,r}^s f = 
\begin{dcases}
\sum_{i = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(D_kf\bigr)(X_i) \cdot \bigl(D_\ell f\bigr)(X_i),~~ & \textrm{if $s$ is even, for $q = s/2$} \\
\sum_{i,j = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(d_jD_kf\bigr)(X_i) \cdot \bigl(d_jD_{\ell}f\bigr)(X_i) \cdot K_r(X_i,X_j),~~ & \textrm{if $s$ is odd, for $q = (s - 1)/2$}
\end{dcases}
\end{equation*}
where $\bigl(d_jf\bigr)(x) := f(X_j) - f(x)$ is the simple difference operator.

In order to prove~\eqref{eqn:graph_sobolev_seminorm}, we will proceed as in Lemma~\ref{lem:first_order_graph_sobolev_seminorm} by first upper bounding $\Ebb[f^T \Lap_{n,r}^s f]$ and then applying Markov's inequality. Obtaining the desired upper bound on $\Ebb[f^T \Lap_{n,r}^s f]$ is split into \textcolor{red}{N} Lemmas, Lemmas \textcolor{red}{A - B}. Lemma~\ref{lem:expected_difference_operator} controls the expectation of the ``leading terms'' $\Ebb[D_kf(x)]$, when $k \in (n)^q$ and $x$ is sufficiently in the interior of $\Xset$. 
\begin{lemma}
	\label{lem:expected_difference_operator}
\end{lemma}

>>>>

\section{Bounds on the graph Sobolev semi-norm}
In this section we will state and prove three different results involving the graph Sobolev semi-norm $f_0 \Lap_{n,r}^s f_0$. In each Lemma, we will derive that the asymptotic relation
\begin{equation*}
f_0^T \Lap_{n,r}^s f_0 \lesssim n \bigl(nr^{d + 2}\bigr)^s
\end{equation*}
holds with high probability, whenever $r \to 0$ sufficiently slowly as $n \to \infty$. The difference between the three results will be the assumptions we make, and the resulting range of permissible values for the radius $r$.

\paragraph{Some facts from calculus.}

The analysis in this section will frequently appeal to Taylor's Theorem, which we now briefly recall in a form convenient for our purposes. For an open set $U \subseteq \Reals^d$ and a function $g \in C^{s}(U)$, it holds that for all $x,x' \in U$,
\begin{equation*}
g(x') = \sum_{\abs{\alpha} = 0}^{s - 1} g^{(\alpha)}(x) \cdot (x' - x)^{\alpha}  + \sum_{\abs{\alpha} = s}R_g^{(\alpha)}(x,x') \cdot (x' - x)^{\alpha}
\end{equation*}
where for $\alpha \in \mathbb{N}^d$ we use the multiindex notation $x^{\alpha} = \prod_{i = 1}^{d} x_i^{\alpha_i}$, and
\begin{equation*}
g^{(\alpha)}(x) = \frac{1}{\abs{\alpha}!} \bigl(D^{\alpha}g\bigr)(x),~~ R_g^{(\alpha)}(x,x') = \frac{1}{\abs{\alpha}!} \int_{0}^{1} (1 - t)^{\abs{\alpha}}  g^{(\alpha)}\bigl(x + t(x' - x)\bigr) \,dt,
\end{equation*}
where we note that the integral form of the remainder is well-defined by Rademacher's theorem. To keep our equations as compact as possible, we also introduce the following notation. For a remainder term $R: U \times U \to \Reals$, let
\begin{align*}
\Bigl(\Ebb_{\alpha}[R]\Bigr)(x) & := \int_{U} (x' - x)^{\alpha} R(x,x') K_r(x,x') p(x') \,dx',~~ && \Ebb_{\alpha}(x) := \Bigl(\Ebb_{\alpha}[1]\Bigr)(x) \\
\Bigl(\Ibb_{\alpha}[R]\Bigr)(x) & := \int_{U} (x' - x)^{\alpha} R(x,x') K_r(x,x') \,dx',~~ && \Ibb_{\alpha}(x)  := \Bigl(\Ibb_{\alpha}[1]\Bigr)(x);
\end{align*}
and
\begin{equation*}
I_{\alpha} := \int_{B(0,1)} (z)^{\alpha} K\bigl(\norm{z}\bigr) \,dz
\end{equation*}
where $B(0,1) \subseteq \Reals^d$ is the unit ball centered at the origin. (It will always be clear from context what the domain $U$ of integration is, and so we suppress it in our notation.)

Let $V \subset U$ satisfy $B(x,r) \subset U$ for all $x \in V$. Before moving on, we will record four facts that will later be of use to us:  first, that $\Ibb_{\alpha}(x) = r^{\abs{\alpha} + d} I_{\alpha}$; second that $I_{\alpha} = 0$ unless $\alpha_i$ is even for all $i \in [d]$; third, that
\begin{equation}
\label{eqn:integrated_remainder_term_sobolev}
\Bigl\|\Ebb_{\alpha}\bigl[R_g^{(\alpha)}\bigr]\Bigr\|_{\Leb^2(V)} \leq p_{\max} K_{\max} r^{\abs{\alpha} + d} \abs{g}_{H^{\abs{\alpha}}(U)}
\end{equation}
and fourth that
\begin{equation}
\label{eqn:integrated_remainder_term_holder}
\Bigl\|\Ebb_{\alpha + \beta}\bigl[R_g^{(\beta)}\bigr]\Bigr\|_{\Leb^{\infty}(V)} \leq p_{\max} K_{\max} r^{\abs{\alpha + \beta} + d} |g|_{C^{\abs{\beta}}(U)}
\end{equation}
The proofs of~\eqref{eqn:integrated_remainder_term_sobolev} and~\eqref{eqn:integrated_remainder_term_holder} are straightforward; for purposes of completeness we provide them in Section~\ref{subsec:proof_integrated_remainder_terms}.
Finally, we note that for $g \in C^{s}(U)$ and $f \in H^s(U)$, 
\begin{equation}
\label{eqn:product_rule_sobolev}
\bigl\|f \cdot g\bigr\|_{H^s(U)} \leq C \norm{g}_{C^s(U)} \norm{f}_{H^s(U)}
\end{equation}
for a constant $C$ which depends only on $s$, but which we will not bother to identify further.

\subsection{First-order graph Sobolev semi-norm.}
We begin by upper bounding $f_0^T \Lap_{n,r} f_0$ under the assumption $f_0 \in H^1(\Xset,M)$. This will be the easiest of the three Lemmas to prove, while still giving some sense of how the proofs develop in the more complicated cases. The upper bound will depend on the kernel $K$; we assume throughout that $K:[0,\infty) \to [0,\infty)$ is a $K_{\max}$-Lipschitz function supported on $[0,1]$, and without loss of generality that
\begin{equation*}
\int_{\Reals^d} K(\norm{z}) \,dz = 1.
\end{equation*}
\begin{lemma}
	\label{lem:first_order_graph_sobolev_seminorm}
	Suppose $\Xset$ is a Lipschitz domain, and that $p(x) \leq p_{\max}$ for all $x \in \Xset$. Then, for any $f \in H^1(\Xset,M)$, there exists a constant $C > 0$ which may depend only on $\Xset$ and $d$ such that
	\begin{equation}
	f^T \Lap_{n,r} f \leq \frac{C}{\delta} n^2 r^{d + 2} M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{lemma}
\begin{proof}
	We will show that
	\begin{equation*}
	\Ebb\Bigl[f^T \Lap_{n,r} f\Bigr] \leq C n^2 r^{d + 2} M^2,
	\end{equation*}
	whence the claim follows immediately by Markov's inequality (recall that $\Lap_{n,r}$ is positive semi-definite, and therefore $f^T \Lap_{n,r} f$ is a non-negative random variable).

@@

\subsection{Order-$s$ graph Sobolev semi-norm}

When $s > 1$, in order to obtain the desired upper bound on the graph Sobolev semi-norm we must make some additional assumptions regarding the behavior of $f_0$ near the boundary of $\Xset$, as well as on the smoothness of the density function $p$.
\begin{theorem}
	\label{thm:graph_sobolev_seminorm}
	For some integer $s > 1$, suppose that the density $p \in C^{s - 1}(\Xset,p_{\max})$ and $f \in H_0^s(\Xset,M)$, and additionally that the domain $\Xset$ is Lipschitz. Let $r = r(n)$ be a sequence of connectivity radii satisfying $r(n) \to 0$ and $r(n) \gtrsim n^{-1/(2(s - 1) +d)}$ as $n \to \infty$. Then for all $n$ sufficiently large, there exists a constant $C > 0$ which may depend only on $\Xset$ and $d$ such that
	\begin{equation}
	\label{eqn:graph_sobolev_seminorm}
	f^T \Lap_{n,r}^s f \leq \frac{C}{\delta} n^{s + 1} r^{s(d + 2)}M^2
	\end{equation}
	with probability at least $1 - \delta$.
\end{theorem}
A few remarks:
\begin{itemize}
	\item \textbf{Explain why~\eqref{eqn:graph_sobolev_seminorm} should be familiar, and a lower bound on $r$ expected.} The scaling (in $n$, $r$, and $M$) on the right hand side of~\eqref{eqn:graph_sobolev_seminorm} will be familiar to the informed reader. For sufficiently regular functions $f$, it is known \textcolor{red}{(references)} that $\frac{1}{nr^{d + 2}}\Lap_{n,r}f \to \Delta_pf$ for \textcolor{red}{$r \geq ???$}. In that light, it is perhaps reasonable to hope that when $r$ is sufficiently large, some recursive argument yields
	\begin{equation*}
	\Bigl(\frac{1}{nr^{d + 2}}\Lap_{n,r}\Bigr)^s f \to \Delta_p^qf \Longrightarrow \frac{1}{n^{s + 1} r^{s(d + 2)}} f^T \Lap_{n,r}^s f \to \int_{\Xset} f(x) \cdot  \Delta_p^qf(x) p(x) \,dx \leq c M^2.
	\end{equation*}
	\item \textbf{Explain why the actual proof is more subtle.}
\end{itemize}
The proof of Theorem~\ref{thm:graph_sobolev_seminorm} will be considerably longer than that of Lemma~\ref{lem:first_order_graph_sobolev_seminorm}. In anticipation of this proof, it will be helpful to introduce some notation. For $j \in [n]$ and a function $f: \Xset \to \Reals$, define the weighted difference operator $D_jf: \Xset \to \Reals$ to be
\begin{equation*}
\bigl(D_jf\bigr)(x) = \bigl(f(X_j) - f(x)\bigr) \frac{K_r(X_j,x)}{r^d},
\end{equation*}
and for $k \in [n]^q$ for some $q \in \mathbb{N}$, define the iterated difference operator $D_{jk}f: \Xset \to \Reals$ via the recursive relation
\begin{equation*}
\bigl(D_{jk}f\bigr)(x) = \bigl(D_j \circ D_kf\bigr)(x)
\end{equation*}
The matrix $\Lap_{n,r} \in \Reals^{n \times n}$ can then be extended to an operator over $C^{\infty}(\Xset)$, which in an abuse of notation\footnote{We repeat notation because it results in \eqref{eqn:graph_Laplacian_out_of_sample} agreeing with \textcolor{red}{(2)} in-sample, i.e. $\bigl(\Lap_{n,r}^qf\bigr)(X_i) = (\Lap_{n,r}^qf)_i$ for all $i \in [n]$.} we also denote by $\Lap_{n,r}$,
\begin{equation*}
\frac{1}{r^d}\bigl(\Lap_{n,r}f\bigr)(x) := -\sum_{j = 1}^{n} \bigl(D_jf\bigr)(x)
\end{equation*}
so that
\begin{equation}
\label{eqn:graph_Laplacian_out_of_sample}
\frac{1}{r^{dq}}\bigl(\Lap_{n,r}^qf\bigr)(x) = (-1)^q \sum_{k \in [n]^q} \bigl(D_kf\bigr)(x).
\end{equation} 
Consequently, a few standard computations show that the graph Sobolev semi-norm can be written as 
\begin{equation}
\label{eqn:graph_sobolev_seminorm_1}
f^T \Lap_{n,r}^s f = r^{ds} \cdot
\begin{dcases}
\sum_{i = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(D_kf\bigr)(X_i) \cdot \bigl(D_\ell f\bigr)(X_i),~~ & \textrm{if $s$ is even, for $q = s/2$} \\
\sum_{i,j = 1}^{n} \sum_{k \in [n]^q} \sum_{\ell \in [n]^q} \bigl(d_jD_kf\bigr)(X_i) \cdot \bigl(d_jD_{\ell}f\bigr)(X_i) \cdot K_r(X_i,X_j),~~ & \textrm{if $s$ is odd, for $q = (s - 1)/2$}
\end{dcases}
\end{equation}
where $\bigl(d_jf\bigr)(x) := f(X_j) - f(x)$ is the simple difference operator.

In order to prove~\eqref{eqn:graph_sobolev_seminorm}, we will proceed as we did in proving Lemma~\ref{lem:first_order_graph_sobolev_seminorm}: we first upper bound $\Ebb[f^T \Lap_{n,r}^s f]$, and then apply Markov's inequality. From the representation~\eqref{eqn:graph_sobolev_seminorm_1} we gather that to analyze the expected graph Sobolev seminorm, it suffices to evaluate the expectation of products of iterated difference operators, and we do the latter in Lemmas \textcolor{red}{A - B} which we now state.

Let $\Delta_r$ be the expected weighted difference operator
\begin{equation}
\Delta_rf(x) := \Ebb\Bigl[\bigl(D_if\bigr)(x)\Bigr] = -\frac{1}{r^d}\int_{\Xset} \bigl(f(x') - f(x)\bigr) K_r(x',x) p(x') \,dx
\end{equation}
and define $\Delta_r^q = \Delta_r \circ \cdots \circ \Delta_r$, with the operator $\Delta_r$ being composed a total of $q$ times. Lemma~\ref{lem:expected_difference_sobolev} shows that when $k \in (n)^q$, the iterated expected weighted difference operator $\Delta_r^qf$ approximates the iterated Laplace operator $\Delta_p^qf$ (after an appropriate rescaling), averaged over points $x$ sufficiently far from the boundary of $\Xset$. Lemma~\ref{lem:expected_difference_boundary} shows that when $k \in (n)^q$, the zero-trace condition implies that $\Delta_r^qf$ is itself small, averaged over points $x$ near the boundary of $\Xset$. In Lemmas~\ref{lem:expected_difference_lower_order_1} and~\ref{lem:expected_difference_lower_order_2}, we take care of those remaining terms, where there is at least one repeated index in the iterated weighted difference operator.

\begin{lemma}
	\label{lem:expected_difference_sobolev}
	Let $q \geq 1$ and $s \geq 2q + 1$ be integers. The iterated expected weighted difference operator  $\Delta_r^qf(x) = \Ebb[D_kf(x)]$ for any $k \in (n)^q$. If $f \in H^s(\Xset,M)$ and $p \in C^{s-1}(\Xset,M)$,
	\begin{equation*}
	\Bigl\|\Delta_r^qf - \bigl(r^{2q} I_{2e_1}^{q}\bigr) \Delta_{p}^qf\Bigr\|_{\Leb^2(\Xset_{qr})} \leq CM \cdot
	\begin{dcases}
	r^{2q + 1},& ~~\textrm{if $s = 2q + 1$} \\
	r^{2q + 2},& ~~\textrm{if $s = 2q + 2$}
	\end{dcases}
	\end{equation*}
	where $\Xset_{qr} = \{x \in \Xset: B(x,qr) \subset \Xset\}$, and we recall that $\Delta_pf = -\frac{1}{2p}\mathrm{div}(p^2 \nabla f)$ is the density weighted Laplace operator.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_boundary}
	Let $q \geq 1$ and $s \geq 1$ be integers. If $f \in H_0^s(\Xset,M)$ and \textcolor{red}{$p$ satisfies (P2)}, then for all $r > 0$ sufficiently small,
	\begin{equation*}
	\norm{\Delta_r^qf}_{\Leb^2(\Xset^{qr})} \leq cMr^s
	\end{equation*}
	where $\Xset^{qr} = \Xset \setminus \Xset_{qr}$.
\end{lemma}
\begin{lemma}
	\label{lem:expected_difference_lower_order_1}
	Let $I = \abs{k \cup \ell \cup i} < 2q + 1$ for given index vectors $k,\ell \in [n]^q$ and index $i \in [n]$. Then for any $f \in H^1(\Xset)$,
	\begin{equation*}
	\Bigl|\Ebb\Bigl[\bigl(D_kf\bigr)(X) \cdot \bigl(D_{\ell}f\bigr)(X)\Bigr]\Bigr| \leq C r^{2 + d(I - (s + 1))} \abs{f}_{H^1(\Xset)}^2
	\end{equation*}
	for a constant $C$ which does not depend on $f$.
\end{lemma}
A few remarks:
\begin{itemize}
	\item In~\textcolor{red}{Garcia-Trillos19}, results similar to Lemma~\ref{lem:expected_difference_sobolev} were shown, as part of the proof of pointwise convergence of the graph Laplacian $\Lap_{n,r}$ to $\Delta_p$. Those results specialize to the case $q = 1$ and $s = 3$, and assume the function $f$ is bounded in the relevant Holder rather than Sobolev norm, sufficient for their purposes but not for our own. 
	\item When the function $f$ lacks sufficiently regularity---i.e. when it has two or fewer bounded derivatives---we can no longer obtain an estimate of  $\Delta_rf$ in terms of $\Delta_pf$. However, we can still show that $\Delta_rf$ is itself bounded. For an open set $V \subseteq \Xset$, if $f \in H^{s}(V,M)$---and when $s = 2$, $p \in C^{1}(\Xset,M)$---then
	\begin{equation}
	\label{eqn:norm_expected_difference_operator}
	\norm{\Delta_rf}_{\Leb^2(V_r)} \leq c r^s \norm{f}_{H^s(V)}
	\end{equation}
	for $V_r = \set{x \in V: B(x,r) \subset V}$. We establish this fact, and bound a few related integrals, in Subsection~\ref{subsec:proof_boundedness_expected_difference_operator}.
	\item \textbf{Discuss how the analysis in \textcolor{red}{Belkin12} could conceivably lead to similar conclusions as Lemma~\ref{lem:expected_difference_boundary} under a milder assumption than zero-trace. Explain why you didn't bother to go down this road.}
\end{itemize}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:expected_difference_sobolev}}.]
	Without loss of generality we will assume $f \in C^{\infty}(\Xset)$ and $p \in C^{\infty}(\Xset)$, as justified in the proof of Theorem~\ref{thm:graph_sobolev_seminorm}.

	We will actually prove a more general claim. Let $f \in C^{\infty}(\Xset)$ additionally satisfy $f \in H^s(\Vset,M)$ for an open set $\Vset \subset \Xset$, and let $s \geq 2q + 1$. Letting $\Vset_{qr} = \{x \in \Vset: B(x,qr) \subseteq \Vset\}$, we will show that there exist functions $f_{2t} \in H^{s - 2t}(\Vset_{qr},CM)$ for $t = q + 1,\ldots,\floor{(s - 1)/2}$ such that
	\begin{equation}
	\label{pf:expected_difference_sobolev_0}
	\Bigl\| \Delta_r^q f  - \bigl(r^{2q} I_{2e_1}^q\bigr) \Delta_p^q f - \sum_{t = q + 1}^{\floor{(s - 1)/2}} r^{2t}f_{2t} \Big\|_{\Leb^2(\Vset_{qr})} \leq C M r^s
	\end{equation}
	for a constant $C$ which depends only on $\Vset$, $d$, $s$, and $p_{\max}$.  We note that in our proof the functions $f_u$ may differ from line to line, but they will always satisfy $f_u \in H^{s - u}(\Vset_{qr},M)$. To see that~\eqref{pf:expected_difference_sobolev_0} implies the claim of the Lemma, simply take $\Vset = \Xset$, and note that when $s = 2q + 1$ or $s = 2q + 2$, the sum on the left hand side of~\eqref{pf:expected_difference_sobolev_0} is empty.

	We proceed by induction on $q$. When $q = 1$, the expected difference operator
	\begin{equation*}
	\Delta_r^qf(x) = \Delta_rf(x) = -\frac{1}{r^d} \int_{\Xset} \bigl(f(x') - f(x)\bigr) K_r(x',x) p(x') \,dx' =  -\frac{1}{r^d} \int_{\Vset} \bigl(f(x') - f(x)\bigr) K_r(x',x) p(x') \,dx'
	\end{equation*}
	where we may restrict the integral to $\Vset$ since $B(x,r) \subset \Vset$ and $K$ has support on $[0,1]$. Taking Taylor expansions of $f$ and $p$ around $x' = x$, and writing things in our compact notation, we have
	\begin{align}
	\bigl(\Delta_rf\bigr)(x) & = -\frac{1}{r^d} \Biggl\{ \sum_{\abs{\alpha} = 1}^{s - 1} f^{(\alpha)}(x) \Ebb_{\alpha}(x) + \sum_{\abs{\alpha} = s}\Bigl(\Ebb_{\alpha}\bigl[R_f^{(\alpha)}\bigr]\Bigr)(x) \Biggr\}  \nonumber\\
	& = -\frac{1}{r^d} \Biggl\{ \sum_{\abs{\alpha} = 1}^{s - 1} f^{(\alpha)}(x) \biggl[ \sum_{\abs{\beta} = 0}^{s - 2} p^{(\beta)}(x) \Ibb_{\alpha + \beta}(x) + \sum_{\abs{\beta} = s - 1} \Bigl(\Ibb_{\alpha + \beta}\bigl[R_p^{(\beta)}\bigr]\Bigr)(x)  \biggr] + \sum_{\abs{\alpha} = s}\Bigl(\Ebb_{\alpha}\bigl[R_f^{(\alpha)}\bigr]\Bigr)(x) \Biggr\} \nonumber \\
	& = - \sum_{\abs{\alpha} = 1}^{s - 1}  \sum_{\abs{\beta} = 0}^{s - 2}  f^{(\alpha)}(x) p^{(\beta)}(x) I_{\alpha + \beta} r^{\abs{\alpha + \beta}} - \frac{1}{r^d} \Biggl\{\sum_{\abs{\alpha} = 1}^{s - 1} \sum_{\abs{\beta} = s - 1} f^{(\alpha)}(x)\Bigl(\Ibb_{\alpha + \beta}\bigl[R_p^{(\beta)}\bigr]\Bigr)(x)+ \sum_{\abs{\alpha} = s}\Bigl(\Ebb_{\alpha}\bigl[R_f^{(\alpha)}\bigr]\Bigr)(x) \Biggr\} \nonumber \\
	& = \sum_{u = 1}^{2s - 3} f_u(x) r^{u} - \frac{1}{r^d} \Biggl\{\sum_{\abs{\alpha} = 1}^{s - 1} \sum_{\abs{\beta} = s - 1} f^{(\alpha)}(x)\Bigl(\Ibb_{\alpha + \beta}\bigl[R_p^{(\beta)}\bigr]\Bigr)(x)+ \sum_{\abs{\alpha} = s}\Bigl(\Ebb_{\alpha}\bigl[R_f^{(\alpha)}\bigr]\Bigr)(x) \Biggr\} \label{pf:expected_difference_sobolev_1}
	\end{align}
	where the final equality follows by putting
	\begin{equation}
	\label{pf:expected_difference_sobolev}
	f_u(x) = - \sum_{\abs{\alpha} + \abs{\beta} = u} I_{\alpha + \beta} f^{(\alpha)}(x) p^{(\beta)}(x),
	\end{equation}
    where the sum is over indices $1 \leq \abs{\alpha} \leq s - 1$ and $0 \leq \abs{\beta} \leq s - 2$.

	The remainder terms---those inside the braces in~\eqref{pf:expected_difference_sobolev_1}--have $\Leb^2(V_r)$ norm on the order of at most $r^s$; when $\alpha = \abs{s}$
	\begin{equation*}
	\frac{1}{r^d} \Bigl\|\Ebb_{\alpha}\bigl[R_f^{(\alpha)}\bigr]\Bigr\|_{\Leb^2(\Vset_r)} \leq p_{\max} K_{\max} M r^s
	\end{equation*}
	follows directly from~\eqref{eqn:integrated_remainder_term_sobolev}, and when $\abs{\alpha} \geq 1$ and $\abs{\beta} = s - 1$,
	\begin{equation*}
	\frac{1}{r^d} \Bigl\|f^{(\alpha)} \cdot \Ibb_{\alpha + \beta}\bigl[R_p^{(\beta)}\bigr]\Bigr\|_{\Leb^2(\Vset_r)} \leq \frac{1}{r^d}\Big\|f^{(\alpha)} \Bigr\|_{\Leb^2(\Vset_r)} \Big\|\Ibb_{\alpha + \beta}\bigl[R_p^{(\beta)}\bigr]\Bigr\|_{\Leb^{\infty}(\Vset_r)} \leq p_{\max} K_{\max} M r^s
	\end{equation*}
	follows from~\eqref{eqn:integrated_remainder_term_holder}.

	It remains to deal with the functions $f_u$. Whenever $\abs{\alpha + \beta} = u$ is odd, $I_{\alpha + \beta} = 0$; as a result $f_u = 0$ for all $u$ odd. When $u = 2$, $I_{\alpha + \beta}$ is non-zero only if either $\alpha = \beta = e_i$ for some $i \in [d]$, or $\alpha = 2e_i$ and $\beta = 0$. So the leading term becomes
	\begin{equation*}
	f_2(x) = \sum_{i = 1}^{d} I_{2e_i}\Bigl\{\frac{1}{2}f^{(2e_i)}(x)p(x) + f^{(e_i)}(x)p^{(e_i)}(x)\Bigr\} = I_{2e_1} \cdot \Delta_pf(x).
	\end{equation*}
	Next, if $4 \leq \abs{\alpha + \beta} = u \leq s$ and $\abs{\beta} \leq u - 1$, then 
	\begin{equation*}
	f^{(\alpha)} \in H^{s - \abs{\alpha}}(\Xset,M) \subseteq H^{s - u}(\Vset_r,M) ~~\textrm{and}~~ p^{(\beta)} \in C^{(s - 1) - \abs{\beta}}(\Xset,p_{\max}) \subset C^{s - u}(\Vset_r,p_{\max})
	\end{equation*}
	which along with~\eqref{pf:expected_difference_sobolev} verifies $f_u \in H^{s - u}(\Vset_r,cM)$ for a constant $c$ which does not depend on $f$ or $M$. Finally, if $\abs{\alpha + \beta} = u > s$ then 
	\begin{equation*}
	f^{(\alpha)} \in \Leb^2(\Xset,M) \subseteq \Leb^2(\Vset_r,M) ~~\textrm{and}~~ p^{(\beta)} \in \Leb^{\infty}(\Xset,p_{\max}) \subseteq \Leb^{\infty}(\Vset_r,p_{\max})
	\end{equation*}
	and so $f_u \in \Leb^2(\Vset_r,cM)$. Hence we have proved~\eqref{pf:expected_difference_sobolev_0} in the base case $q = 1$.

	Now for the induction step. Suppose $f \in H^s(\Vset,cM)$ for $s \geq 2(q + 1) + 1$. Since $\Delta_r^{(q + 1)}f = \Delta_r \circ \Delta_r^qf$, applying the inductive hypothesis to $\Delta_r^qf$ gives
	\begin{equation}
	\label{pf:expected_difference_sobolev_2}
	\Bigl\| \Delta_r^{(q + 1)}f - r^{2q}I_{2e_1}^q\Delta_r(\Delta_p^qf) + \sum_{t = q + 1}^{\floor{(s - 1)/2}}r^{2t} \Delta_r(f_{2t}) \Bigr\|_{\Leb^2(\Vset_{(q + 1)r})} \leq c M r^s
	\end{equation}
	Looking at those terms $\Delta_r(f_{2t})$, when $2t \leq s  - 3$ then $f_{2t} \in H^{s - 2t}(\Vset_{qr},cM) \subset H^3(\Vset_{qr},cM)$ and it follows from the inductive hypothesis that
	\begin{equation*}
	\biggl\| r^{2t}\Delta_r(f_{2t}) - r^{2(t + 1)}I_{2e_1}\Delta_p(f_{2t}) - \sum_{h = 2}^{\floor{(s - 2t - 1)/2}}r^{2(t + h)}f_{2t + 2h}\biggr\|_{\Leb^2(\Vset_{(q + 1)r})} \leq c M r^{2t + (s  - 2t)}.
	\end{equation*}
	We note that $\Delta_p(f_{2t}) \in H^{s - 2(t + 1)}(\Vset_{qr},cM)$, and we may therefore write the above expression more succinctly,
	\begin{equation}
	\label{pf:expected_difference_sobolev_3}
	\biggl\| r^{2t}\Delta_r(f_{2t}) - \sum_{h = t + 1}^{\floor{(s - 1)/2}}r^{2h}f_{2h}\biggr\|_{\Leb^2(\Vset_{(q + 1)r})} \leq c M r^{s}.
	\end{equation}
	On the other hand, when $2t = s - 2$ or $2t = s - 1$, it follows directly  from~\eqref{eqn:norm_expected_difference_operator} that
	\begin{equation}
	\label{pf:expected_difference_sobolev_4}
	\Bigl\|r^{2t}\Delta_r(f_{2t})\Bigr\|_{\Leb^2(\Vset_{qr})} \leq c  r^{2t + (s - 2t)} \norm{f_{2t}}_{H^{s - 2t}(\Vset_{qr})} \leq c M r^{s}.
	\end{equation}
